Primers

### 2017-12-06 inst/primers/primers.Rmd
adding primer document

---
title: "Primers used in the miR34a asRNA study"
output:
  pdf_document:
  html_document:
    theme: flatly
    toc: no
    code_folding: hide
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(message=FALSE, 
tidy.opts=list(width.cutoff=60))
library(pander)
```

```{r, echo=FALSE}
d1 <- data.frame(
    name="miR155_asF",
    sequence="AAG CTG GTC CAG\nGGC CAT TAT ACA",
    figures="Supplementary Fig. 1A"
)

d2 <- data.frame(
    name="miR155_asR",
    sequence="TGA CCT CAT GAT CCA GTC ACC TCA",
    figures="Supplementary Fig. 1A"
)

d3 <- data.frame(
    name="miR301a_asF2",
    sequence="CAA CGG CAG AAG CTT CAC CAC AAA",
    figures="Supplementary Fig. 1A"
)

d4 <- data.frame(
    name="miR301a_asR2",
    sequence="CGC TGC TGG ATT CGT TTG GCA TAA",
    figures="Supplementary Fig. 1A"
)

d5 <- data.frame(
    name="miR34bc_asF2",
    sequence="ACA GAA GTC ACT GGC ACT CTG A",
    figures="Supplementary Fig. 1A"
)

d6 <- data.frame(
    name="miR34bc_asR2",
    sequence="ACC CAT ATG GTC ATC TCC TTC GGA",
    figures="Supplementary Fig. 1A"
)

d7 <- data.frame(
    name="miR21_asF",
    sequence="AGT CTT ACC TGT GGT GTG CCC ATT",
    figures="Supplementary Fig. 1A"
)

d8 <- data.frame(
    name="miR21_asR",
    sequence="AGG TCC ATC TCT GCA GAA GCC ATT",
    figures="Supplementary Fig. 1A"
)

d9 <- data.frame(
    name="miR29b_asF",
    sequence="TGT AAT AAG AAG GGC GGT GCT CGT",
    figures="Supplementary Fig. 1A"
)

d10 <- data.frame(
    name="miR29b_asR",
    sequence="AAC CTG TCT TTG TCG CAG GTC TCA",
    figures="Supplementary Fig. 1A"
)

d11 <- data.frame(
    name="miR142_asRNA_F",
    sequence="TTG ATC GTC ATG CTG ACC CAG TGA",
    figures="Supplementary Fig. 1A"
)

d12 <- data.frame(
    name="miR142_asRNA_R",
    sequence="GGG CGG TCT TAC ATG CCT TTG AAT",
    figures="Supplementary Fig. 1A"
)

d13 <- data.frame(
    name="miR34a_asF10",
    sequence="ACG CGT CTC TCC AGC CCG GGA T",
    figures="Fig. 1C, Fig. 1E"
)

d14 <- data.frame(
    name="miR34a_asF11",
    sequence="ATC TGC GTG GTC ACC GAG AAG CA",
    figures="Fig. 1E"
)

d15 <- data.frame(
    name="miR34a_asF12",
    sequence="AAA CAC AAG CGT TTA CCT GGG TGC",
    figures="Fig. 1E, Supplementary Fig. 1C"
)

d16 <- data.frame(
    name="miR34a_asF13",
    sequence="ACG GAG GCT ACA CAA TTG AAC AGG",
    figures="Fig. 1E"
)

d17 <- data.frame(
    name="miR34a_asF14",
    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
    figures="Fig. 1E"
)

d18 <- data.frame(
    name="miR34a_asF15",
    sequence="CAT TTG CTG CAA TAT CAC CGT GGC",
    figures="Fig. 1E"
)

d19 <- data.frame(
    name="miR34a_as_int1R1",
    sequence="TGC GCA AAC TAC GCG CTC T",
    figures="Fig. 1F"
)

d20 <- data.frame(
    name="miR34a_asR2",
    sequence="ATA GGT TCA TTT GCC CGA TGT GCC",
    figures="Supplementary Fig. 1C"
)

d21 <- data.frame(
    name="miR34a_asR3",
    sequence="CCA CAG CTG TTG CTT CTG AAT GCT",
    figures="Supplementary Fig. 1C"
)

d22 <- data.frame(
    name="miR34a_asEx3_R1",
    sequence="GTT GCC TTC TTC GCA ACT CCT TGT",
    figures="Supplementary Fig. 1C"
)

d23 <- data.frame(
    name="miR34a_asF1",
    sequence="AGC GGC ATC TCC TCC ACC TGA AA",
    figures="Fig. 1B, Fig. 1C, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d24 <- data.frame(
    name="miR34a_asR1",
    sequence="TTG CCT CGT GAG TCC AAG GAG AAT",
    figures="Fig. 1B, Fig. 1E, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3B, Supplementary Fig. 1B, Supplementary Fig. 1C, Supplementary Fig. 1E"
)

d25 <- data.frame(
    name="miR34a_HG_F",
    sequence="TCT GCT CCA GTG GCT GAT GAG AAA",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
)

d26 <- data.frame(
    name="miR34a_HG_R",
    sequence="GTT CAC TGG CCT CAA AGT TGG CAT",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B"
)

d27 <- data.frame(
    name="miR34a_mature_F",
    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
    figures="Fig. 3B"
)

d28 <- data.frame(
    name="miR34a_mature_R",
    sequence="TaqMan® MicroRNA Assay, hsa-miR-34a, human",
    figures="Fig. 3B"
)

d29 <- data.frame(
    name="B-actin_F",
    sequence="AGG TCA TCA CCA TTG GCA ATG AG",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d30 <- data.frame(
    name="B-actin_R",
    sequence="CTT TGC GGA TGT CCA CGT CA",
    figures="Fig. 1B, Fig. 1F, Fig. 1G, Fig. 1H, Fig. 2A, Fig. 2B, Fig. 3A, Fig. 3B, Fig. 3D, Supplementary Fig. 1B, Supplementary Fig. 1E"
)

d31 <- data.frame(
    name="T7_long_reverse",
    sequence="CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
    figures="Fig. 1C"
)

d32 <- data.frame(
    name="FAM_primer",
    sequence="CCG TAG CTC GTC CAG GAC CC",
    figures="Fig. 1C"
)

d33 <- data.frame(
    name="U48_F (sybr)",
    sequence="AGT GAT GAT GAC CCC AGG TA",
    figures="Fig. 1F, Fig. 1G"
)

d34 <- data.frame(
    name="U48_R (sybr)",
    sequence="GGT CAG AGC GCT GCG GTG AT",
    figures="Fig. 1F, Fig. 1G"
)

d35 <- data.frame(
    name="U48_F (taqman)",
    sequence="Control miRNA Assay, RNU48, human",
    figures="Fig. 3B"
)

d36 <- data.frame(
    name="U48_R (taqman)",
    sequence="Control miRNA Assay, RNU48, human",
    figures="Fig. 3B"
)

d37 <- data.frame(
    name="Renilla_pBiDir_F1",
    sequence="TAA CGC GGC CTC TTC TTA TTT",
    figures="Fig. 3A"
)

d38 <- data.frame(
    name="Renilla_pBiDir_R1",
    sequence="GAT TTG CCT GAT TTG CCC ATA",
    figures="Fig. 3A"
)

d39 <- data.frame(
    name="Luc_set_II_F",
    sequence="AAG ATT CAA AGT GCG CTG CTG",
    figures="Fig. 3A"
)

d40 <- data.frame(
    name="Luc_set_II_R",
    sequence="TTG CCT GAT ACC TGG CAG ATG",
    figures="Fig. 3A"
)

d41 <- data.frame(
    name="CCND1 Fwd",
    sequence="CGT GGC CTC TAA GAT GAA GG",
    figures="Fig. 3D"
)

d42 <- data.frame(
    name="CCND1 Rev",
    sequence="CTG GCA TTT TGG AGA GGA AG",
    figures="Fig. 3D"
)

d43 <- data.frame(
    name="miR34a ChIP_F1",
    sequence="AAA GTT TGC AAA GAA GGA GGC GGG",
    figures="Fig. 3F"
)

d44 <- data.frame(
    name="miR34aChIP_R1",
    sequence="AGG GAA GAA AGA ACT AGC CGA GCA",
    figures="Fig. 3F"
)

primers <- rbind(
    d1, d2, d3, d4, d5, d6, d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18, d19, d20,
    d21, d22, d23, d24, d25, d26, d27, d28, d29, d30, d31, d32, d33, d34, d35, d36, d37, d38, d39, d40,
    d41, d42, d43, d44
)

primers$primerType <- c(
    rep("Other asRNA", 12),
    rep("miR34a asRNA", 12),
    rep("miR34a HG", 2),
    rep("miR34a mature", 2),
    rep("Other primers", 14),
    rep("miR34a asRNA", 2)
)
primers <- primers[order(as.character(primers$primerType)),]

primers$primerType <- c(
    "miR34a asRNA", rep("", 13),
    "miR34a HG", "",
    "miR34a mature", "",
    "Other asRNA", rep("", 11),
    "Other primers", rep("", 13)
)

colnames(primers) <- c("Name", "Sequence", "Figure", "Primer type")
rownames(primers) <- 1:nrow(primers)
primers <- primers[,c("Primer type", "Name", "Sequence", "Figure")]
```

```{r, results='asis', echo=FALSE}
panderOptions('table.split.table', Inf)
pandoc.table(primers, keep.line.breaks = TRUE)
```

>>>>

---
title: "Primers"
author: "Jason T. Serviss"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    code_folding: hide
    keep_md: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}

library(printr)
library(tibble)

```

## Figure 1b

```{r}

tibble(
    name=c(
        "miR34a asRNA F1",
        "miR34a asRNA R1",
        "miR34a HG F",
        "miR34a HG R",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

## Figure 1d

```{r}

tibble(
  name = c(
    "miR34a asRNA F10",
    "polyT T7 FAM",
    "miR34a asRNA F1",
    "FAM primer"),
  sequence = c(
    "ACG CGT CTC TCC AGC CCG GGA T",
    "CAG TGA ATT GTA ATA CGA CTC ACT ATA GGG ACA TCC GTA GCT CGT CCA GGA CCC TTT TTT TTT TTT TTT TTT VN",
    "AGC GGC ATC TCC TCC ACC TGA AA",
    "CCG TAG CTC GTC CAG GAC CC"
  )
)

```

## Figure 2a

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG F",
        "miR34a HG R",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

## Figure 2b

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a HG F",
        "miR34a HG R",
        "miR34a as F1",
        "miR34a as R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

## Figure 2c

```{r}

tibble(
    name=c(
        "Luc setII F",
        "Luc setII R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

## Figure 2d

```{r}

tibble(
    name=c(
        "Luc set II F",
        "Luc set II R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

## Figure 3a

Cloning primers

```{r}

tibble(
    name=c(
        "miR34aAS cloning F4",
        "miR34aAS cloning Ex3_1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "AAT GAT GGC CGC AAC TAA TGA CGG"
    )
)

```

QPCR primers

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)

```

## Figure 3d

```{r}

tibble(
    name=c(
        "miR34a ChIP F1",
        "miR34a ChIP R1"
    ),
    sequence=c(
       "AAA GTT TGC AAA GAA GGA GGC GGG",
       "AGG GAA GAA AGA ACT AGC CGA GCA"
    )
)

```

## Figure 1 Supplement 2a

```{r}

tibble(
    name=c(
        "miR34a AS F10",
        "miR34a AS F11",
        "miR34a AS F12",
        "miR34a AS F13",
        "miR34a AS F14",
        "miR34a AS F15",
        "miR34a AS R1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "ATC TGC GTG GTC ACC GAG AAG CA",
        "CGC ACG GAC TGA GAA ACA CAA G",
        "ACG GAG GCT ACA CAA TTG AAC AGG",
        "AGG GAA GAA AGA ACT AGC CGA GCA",
        "CAT TTG CTG CAA TAT CAC CGT GGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT"
    )
)

```

## Figure 1 Supplement 2b

```{r}

tibble(
    name=c(
        "miR34a AS F1",
        "miR34a AS R1",
        "miR34a AS int1 R1",
        "miR34a HG F",
        "miR34a HG R",
        "ß-actin Fwd",
        "ß-actin Rev",
        "U48 F",
        "U48 R"
    ),
    sequence=c(
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "TGC GCA AAC TAC GCG CTC T",
        "TCT GCT CCA GTG GCT GAT GAG AAA",
        "GTT CAC TGG CCT CAA AGT TGG CAT",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA",
        "AGT GAT GAT GAC CCC AGG TA",
        "GGT CAG AGC GCT GCG GTG AT"
    )
)

```

## Figure 1 Supplement 2c

```{r}

tibble(
    name=c(
        "miR34a AS F12",
        "miR34a AS R1",
        "miR34a AS R2",
        "miR34a AS R3",
        "miR34a AS Ex3 R1"
    ),
    sequence=c(
        "AAA CAC AAG CGT TTA CCT GGG TGC",
        "TTG CCT CGT GAG TCC AAG GAG AAT",
        "ATA GGT TCA TTT GCC CGA TGT GCC",
        "CCA CAG CTG TTG CTT CTG AAT GCT",
        "TGA TGG CCG CAA CTA ATG ACG GAT"
    )
)

```

## Figure 2 Supplement 2a

```{r}

 tibble(
    name=c(
        "Luc setII F",
        "Luc setII R",
        "Renilla pBiDir F1",
        "Renilla pBiDir R1",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "AAG ATT CAA AGT GCG CTG CTG",
        "TTG CCT GAT ACC TGG CAG ATG",
        "TAA CGC GGC CTC TTC TTA TTT",
        "GAT TTG CCT GAT TTG CCC ATA",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

## Figure 3 Supplement 1a

Cloning primers

```{r}

tibble(
    name=c(
        "miR34aAS cloning F4",
        "miR34aAS cloning Ex3_1"
    ),
    sequence=c(
        "ACG CGT CTC TCC AGC CCG GGA T",
        "AAT GAT GGC CGC AAC TAA TGA CGG"
    )
)

```

QPCR primers

```{r}

tibble(
    name=c(
        "ß-actin Fwd",
        "ß-actin Rev",
        "miR34a AS F1",
        "miR34a AS R1"

    ),
    sequence=c(
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TCG GGA TGT CCA CGT CA",
        "AGC GGC ATC TCC TCC ACC TGA AA",
        "TTG CCT CGT GAG TCC AAG GAG AAT"

    )
)
```

## Figure 3 Supplement 2a

```{r}

tibble(
    name=c(
        "CCND1 Fwd",	
        "CCND1 Rev",
        "ß-actin Fwd",
        "ß-actin Rev"
    ),
    sequence=c(
        "CGT GGC CTC TAA GAT GAA GG",
        "CTG GCA TTT TGG AGA GGA AG",
        "AGG TCA TCA CCA TTG GCA ATG AG",
        "CTT TGC GGA TGT CCA CGT CA"
    )
)

```

```{r}

```
